Diversification of Australian blind snakes

### 2022-11-17 manuscript.Rmd
modified parts of biogeobear results

Based on our best fitting biogeographic model, the constrained-dispersal matrix DEC+_j_+_x_ model, we inferred tropical grassland biome to be ancestral biome of Australian _Anilios_ (\@ref(fig:fig-biogeobears). 
Likelihood ratio test (LRT) indicates that founder event (parameter *j*) and distance matrix (free parameter *x*) in the more complex model provides statistically significant improvement over the simpler DEC, DEC+*j*, and DEC+*x* models (X^2^, DF = 2, D-statistic = 26.7, p-value < 0.001). 
Our result also supports the hypothesis that the ancestor of the Australian clade first invaded the mesic part of the continent [@marinTracing2013], but exactly where they lived prior to this invasion is equivocal between the Bismarck Archipelago and New Guinea. 
After arriving to Australia in the late Oligocene - early Miocene (~25 MYA), the ancestral _Anilios_ initially diversified rapidly within less than 1 million years. Our analysis is consistent with the conclusion that Australian blindsnakes, like several other Australian squamates, originated from tropical-mesic origins and expanded into the arid zone since the mid-Miocene [@chappleParallel2004;@melvilleEvolutionary2011].

@@

## Ancestral biome reconstruction
- Our result — that the ancestor of Anilios occupied tropical grasslands – is consistent with the result presented in @marinTracing2013. 
- We found transitions from XXX to XXX to be common as have been shown / as opposed to other Australian squamates (CITATIONS)
- Arid zone was not arid until ~20 Million Years ago. Ancestors in deeper time probably occupied temperate or tropical areas that subsequently became the arid zone we know see today. 
- The Australo-Papuan clade seems to have stayed in Australia for the most part but we were not able to include New Guinean endemic _Anilios erycinus_, the only recognised species of _Anilios_ not found in Australia. Therefore, we cannot make any conclusions about transitions between Australia and New Guinea even though at least three species (_A. torresianus_, _A. leucoproctus_, ...) are found in Northern 
Australia Torres Strait Islands, and southern parts of New Guinea.
- Range expansion was important for diversification ...
- Topography dyanmics [@brazModelling2021]
- Solomon Island 40 MYA [@hallCenozoic2002]

>>>>

We identified the DEC+_j_+_x_ model as the most preferred biogeographical history model (delta AICc = -4.47, see Table-supp-BioGeoBEARS). 
Likelihood ratio test (LRT) indicates that both founder events (+*j* parameter) and distance between biome (+x parameter) together provides statistically significant improvement over the simpler DEC model, DEC+x  and DEC+j (X^2^, DF = 2, D-statistic = 26.7, p-value < 0.001). 
We inferred tropical grassland biome to be the ancestral biome of Australian _Anilios_ (\@ref(fig:fig-biogeobears), but the origin of crown *Anilios* is ambiguous.

@@

## Ancestral biome reconstruction
- Our result — that the ancestor of Anilios occupied tropical grasslands – is consistent with the result presented in @marinTracing2013.

- Our result also supports the hypothesis that the ancestor of the Australian clade first invaded the mesic part of the continent [@marinTracing2013], but exactly where they lived prior to this invasion is equivocal between the Bismarck Archipelago and New Guinea.

After arriving to Australia in the late Oligocene - early Miocene (~25 MYA), the ancestral _Anilios_ initially diversified rapidly within less than 1 million years. Our analysis is consistent with the conclusion that Australian blindsnakes, like several other Australian squamates, originated from tropical-mesic origins and expanded into the arid zone since the mid-Miocene [@chappleParallel2004;@melvilleEvolutionary2011].

- We found transitions from XXX to XXX to be common as have been shown / as opposed to other Australian squamates (CITATIONS)
- Arid zone was not arid until ~20 Million Years ago. Ancestors in deeper time probably occupied temperate or tropical areas that subsequently became the arid zone we know see today. 
- The Australo-Papuan clade seems to have stayed in Australia for the most part but we were not able to include New Guinean endemic _Anilios erycinus_, the only recognised species of _Anilios_ not found in Australia. Therefore, we cannot make any conclusions about transitions between Australia and New Guinea even though at least three species (_A. torresianus_, _A. leucoproctus_, ...) are found in Northern 
Australia Torres Strait Islands, and southern parts of New Guinea.
- Range expansion was important for diversification ...
- Topography dyanmics [@brazModelling2021]
- Solomon Island 40 MYA [@hallCenozoic2002]
